\section{Implementation of a counter application}
\label{sec:implementation}
This section will include a short explanation of the counter app as an example application.
It will show the features and define the requirements for an objective comparison.

\subsection{Electron}
\label{subsec:impl:electron}
This subection section will take the findings of~\ref{sec:electron} into action and analyze the development and building process as well as the performance of the executable application.

\subsubsection{Development}
\label{subsubsec:impl:electron:dev}
At this subsubsection the general development process of an Electron application is discussed but also the actual development using the screencast
application as an example.
Are there any templates provided, which dependencies and tools are needed for implemention, debbuging and testing.
Are they already provided by the installer?
Also have a short look at the documentation e.g. are there any guides, community feedback.

\subsubsection{Build}
\label{subsubsec:impl:electron:build}
This subsubsection deals with the whole building process of the example Electron app e.g.\ Package manager, cross-platform support, build tools, build time etc.

\subsubsection{Performance}
\label{subsubsec:impl:electron:performance}
At this subsubsection the actual performance of the example application is analyzed.
Memory consumption, known security issues, bugs, freezes etc.

\subsection{Tauri}\label{subsec:impl:tauri}
This subsection section will take the findings of~\ref{sec:tauri} into action and analyze
the development and building process as well as the performance of the executable application.

\subsubsection{Development}
Same as described in~\ref{subsubsec:impl:electron:dev} for Tauri.
\subsubsection{Build}
Same as described in~\ref{subsubsec:impl:electron:build} for Tauri.
\subsubsection{Performance}
Same as described in~\ref{subsubsec:impl:electron:performance} for Tauri.