\section{Introduction}\label{sec:introduction}
Cross-platform web-frameworks like Electron, Tauri or Flutter provide the possibility of using standard web-technologies like \ac{HTML}, \ac{CSS} and JavaScript or entire web-frameworks
like Angular to develop or migrate classic desktop applications to web applications.
The traditional approach of implementing desktop applications needs the developer to consider different \ac{API} or environments of the major  \ac{OS}s
Windows, Mac and Linux.
In fact, each application has to be implemented multiple times to adapt \ac{OS}-specific requirements and produces redundant code.
In context of consumer applications, the usage of frameworks like Electron allows companies and product owners to develop new target groups.
But it also increases the pool of potential applicants, since they provide web developers technologies and features to implement desktop applications without the knowledge of standard programming languages used for those kind of applications like C/C++ or Java.
Furthermore, institutions or universities and their students benefit from it, because applications can be used by many devices, due to the fact of cross-platform capabilities and decrease costs
since they do not need particular hardware to be executed.

\subsection{Background}\label{subsec:background}
In recent years web-frameworks for building desktop applications have experienced more and more attention, which can be expressed by the number of articles related to such topics or the temporal progression of Google Trends related to this topic.
This is owed to the fact of fundamental advances at web technologies like TypeScript, as an improvement of JavaScript, or frontend frameworks like Angular or React~\cite{pernice:icalepcs2019-wempr006},
which led to a wider use of such technologies for various scenarios.
A lot of every day applications used by computer scientists like Visual Studio Code or GitHub Desktop, but also applications with usage spread over industry sectors
like Microsoft Teams, Skype or Discord and even Social Media applications like WhatsApp or Twitch are implemented utilizing cross-platform web-frameworks.
The trend of using those applications has even grown up since the outbreak of SARS-CoV-2 in early 2020~\cite{Gorbalenya2020} and the enlarged number of employees working from home
as a result of lockdowns all over the world.
This led to an increasing number of cross-platform web-frameworks with different approaches in context of building, security or performance to provide a fast and simple way even for small development teams
to use web-technologies for implementing desktop applications, since their cross-platform capabilities prevent redundant implementation of the same application for different \ac{OS}s.

%Research Questions%
\subsection{Motivation}\label{subsec:motivation}
As mentioned in Chapter~\ref{subsec:background}, various cross-platform web-frameworks came up using different technologies or languages for their backend and frontend core.
One of the oldest and most commonly used frameworks is Electron, which is backed up by several popular applications mentioned before utilizing this framework.
Therefore, Electron has become a standard in context of cross-platform development of desktop applications and almost every new framework invented is benchmarked against it like Flutter~\cite{flutter}, JavaFX~\cite{electron-javafx} or Electron~\cite{electron-nwjs}.
Two years ago a new framework called Tauri was introduced, based on the discontent with Electrons high memory consumption or insecurity by its developers.
It was designed to improve several aspects of Electron, especially in case of performance, memory usage and security~\cite{tauri}.
Since these statements are made by the developers and thus may be subjective, this paper aims to provide an objective overview to the reader of both frameworks, Electron and Tauri.
Therefore, fundamental architecture as well as the frontend and backend core of each framework is explained in detail at Chapter~\ref{sec:electron} for Electron and at Chapter~\ref{sec:tauri} for Tauri.
This technological knowledge is applied by implementing a basic application which will be described in detail at Chapter~\ref{sec:implementation} and analyzes different aspects of both.
To obtain an objective comparison between both frameworks, Chapter~\ref{sec:summary} examines the results of previous Chapters
to isolate advantages and disadvantages to the reader.
At the end of this paper, the comparison results of Chapter ~\ref{sec:summary} are contrasted against the statement of the Tauri developers from~\cite{tauri} and being discussed at Chapter~\ref{sec:conclusion} to provide an unbiased
evaluation of both frameworks.

\subsection{Related Work}\label{subsec:related-work}
An exploratory study of the utilization of different frameworks for desktop apps has worked out that applications developed with cross-platform web-frameworks are made for various kinds of usage~\cite{explorationstudy}.
The authors also empirically documented that those frameworks are mostly used by developer teams with a median size of 1, which is a direct result of the
amount resources classical desktop development consumes.
Nevertheless, they also discovered disadvantages using such web-frameworks, like a high number of used libraries.
This is due to the fact of compensating a lack of features provided by the frameworks.
But also a high ratio of platform-related issues to all issues of 20\%.

The increasing popularity of web-technologies has been shown by~\cite{pernice:icalepcs2019-wempr006}.
Since they identified their native Java Swing desktop application as a bottleneck, the authors decided to replace it with a technology stack providing long term sustainability.
Therefore, they used several web-technologies like AngularJS or Typescript to implement ``a web-based tool for configuring experiments on the National Ignition Factory``~\cite{pernice:icalepcs2019-wempr006}.
But they also came in touch with typical problems of the JavaScript ecosystem like exit or replacement of widely used technologies forcing them to migrate from
AngularJS to its successor Angular.
It has to be mentioned that the authors emphasized the community support especially, in case of migration by providing tools for those cases.

Using Electron as a standard benchmark for cross-platform web-frameworks is corroborated by various papers comparing it to other frameworks like JavaFX~\cite{electron-javafx}, NW.js~\cite{electron-nwjs} or Flutter~\cite{flutter}.
Both authors compared different web-frameworks against Electron.
Although the benchmark of the authors of~\cite{electron-javafx} was made with different \ac{IDE}s and the comparison between Flutter and Electron by~\cite{flutter} was based on a beta version of Flutter,
both pointed out that at the one hand Electron has better performance in case of execution time and CPU consumption and on the other hand it provides more features than the compared frameworks.

